NGO analysis

### 2022-07-31 Dashboard/NGO Analysis dashboard alpha v004.Rmd
Commenting.

    # Based on code in Mastering Shiny
    filename = "report.pdf",
    content = function(file) {
      tempReport <- file.path(tempdir(), "report.Rmd")
      file.copy("report.Rmd", tempReport, overwrite = TRUE)

@@

      # notification
      id <- showNotification(
        "Generating report...",
        duration = NULL,
        closeButton = FALSE
      )
      on.exit(removeNotification(id), add = TRUE)

>>>>

    # Based on code in Mastering Shiny - creating a temporary directory and file
    filename = "report.pdf",
    content = function(file) {
      tempReport <- file.path(tempdir(), "report.Rmd")
      file.copy("report.Rmd", tempReport, overwrite = TRUE)

@@

      # notification - disappears when report generation is complete
      id <- showNotification(
        "Generating report...",
        duration = NULL,
        closeButton = FALSE
      )
      on.exit(removeNotification(id), add = TRUE)
